---
title: "RANN Longitudinal with in-scanner and out-of-scanner indicators"
author: "Seonjoo Lee, Zhiqian Fang"
date: '`r format(Sys.Date(), "%Y-%B-%d")`'
output: 
  html_document:
    toc: TRUE
    code_folding: hide
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(textwidth=3000)
library(dplyr)
library(tidyverse)
library(psych)
library(kableExtra)
library(knitr)
library(Matrix)
library(ggplot2)
library(ggthemes)
library(gridExtra)
library(lavaan)
library(DT)
library(sqldf)
library(stringr)
library(reshape2)
library(table1)
library(sjPlot)
library(arsenal)
#setwd("~/Desktop/Practicum/longitudinalRANN/rcodes/longitudinalRANN_ZF")
#setwd("E:/GoogleDrive/Collaboration/Yaakov/RANN_FU/LCA_RANN/projects/ra_lda_manuscript")
#setwd("~/Google Drive/Collaboration/Yaakov/RANN_FU/LCA_RANN/projects/ra_lda_manuscript")
datadir='../../../../RANN_FU/LCA_RANN/projects/ra_lda_manuscript/data_cleaning/'
load(paste(datadir,"RANN_Fu_data_dtimerged_v4_20200603.Rdata",sep=''))
# colnames(all_completer)[grep('median',colnames(all_completer))]


varlists=c('DgtSym_medianCorRT','PattComp_medianCorRT',
'LetComp_medianCorRT',
'MatReas_PropOnTimeCor',
'PaperFold_PropOnTimeCor', 
'LetSet_PropOnTimeCor',
'LogMem_PropOnTimeCor', 
'PairAssoc_PropOnTimeCor', 
'WordOrder_PropOnTimeCor',
'Syn_PropOnTimeCor', 
'Ant_PropOnTimeCor', 
'PictName_Prop',
'WAIS3matRAW',
'BLKraw',
'WAIS3letnumRAW',
'SRTlts',
'SRTcltr',
'SRTlast',
'WAISRdgtsymRAW',
'TMTAtime',
'STRPcRAW',
'WAISRvocRAW',
'WTARraw',
'AMNARTerr')

rann=rann_dat %>% mutate(Male = ifelse(Gender=='M',1,0)) 
rann[rann$subid == '4370','Age_Followup']<-65

rann = rann%>%
  filter(completer==1) %>%
  mutate(yeardiff = Age_Followup - Age) 
rann %>%filter(yeardiff==0) %>% select(subid, Age, Age_Followup)

rann = rann%>%
  filter(yeardiff>0)

#rann %>% filter(yeardiff ==0)%>% select(subid, Age, Age_Followup)
#rann %>% filter(subid == '4370') %>% select(subid, Age, Age_Followup)

for (j in 1:24){
  funame=paste(varlists[j],'_fu',sep='')
  blname=paste(varlists[j],'_bl',sep='')
  rann[,funame] = (rann[,funame] - mean(rann[,blname],na.rm=TRUE))/sd(rann[,blname],na.rm=TRUE)
  rann[,blname] = scale(rann[,blname])
}

## leisure
library(foreign)
leisuredat = data.frame(read.spss('../../../data/Leisure_data_SEM_2021_11_02.sav')) %>%
  select(SubID, Sex,Ed_bl, FamInc, L18_Total_s, L_Cognitive_6_s, L_Physical_2_s, L_Social_6_s) %>%
  rename(subid=SubID)

rann2 = left_join(rann, leisuredat) %>%
  mutate(anal_include = ifelse(is.na(L18_Total_s)==FALSE,1,0)) %>%
  mutate(anal_include2 = ifelse(is.na(L18_Total_s)==FALSE & is.na(FamInc)==FALSE,1,0)) %>%
  mutate(L18_Total_sXGender = L18_Total_s * ifelse(Gender=='M',1,0))

rann$subid[rann$subid %in% leisuredat$subid]
```

```{r, include=FALSE}
source('lcsm_models_nprann_together_leisure.R')
rann.scale=rann2%>% mutate(Age=scale(Age), NARTIQ_bl=scale(NARTIQ_bl), Education_bl = scale(Education_bl))

fit.m1_age<-sem(nprann.m1_age,data=rann.scale,missing='FIML')
fit.m1_total<-sem(nprann.m1_total,data=rann.scale,missing='FIML')
fit.m1_cog<-sem(nprann.m1_cog,data=rann.scale,missing='FIML')
fit.m1_phy<-sem(nprann.m1_phy,data=rann.scale,missing='FIML')
fit.m1_soc<-sem(nprann.m1_soc,data=rann.scale,missing='FIML')
fit.m1_totalxgender<-sem(nprann.m1_totalxgender,data=rann.scale,missing='FIML')
```

# Table2 {.tabset}

## Age + Baseline LA {.tabset}

### Parameters

```{r,fig.width=12, fig.height=6}
kable(rbind(parameterestimates(fit.m1_age,standardized = TRUE) %>% filter(lhs %in% c('flcs','slcs','mlcs','vlcs') & op == '~1') %>% select(-std.lv, -std.nox,-label),parameterestimates(fit.m1_age,standardized = TRUE) %>% filter(lhs %in% c('flcs','slcs','mlcs','vlcs') & op=='~') %>% select(-std.lv, -std.nox,-label)
),
digits=3) %>%
  kable_styling(c("striped", "bordered"), full=F)
  
kable(t(data.frame(fit=fitMeasures(fit.m1_age, c('cfi','tli','bic','rmsea','rmsea.ci.lower','rmsea.ci.upper','rmsea.pvalue')))),digits=3)%>%
  kable_styling(c("striped", "bordered"), full=F)
```

### Full summary
```{r}
summary(fit.m1_age)
```


## Age + Baseline LA + Covariates {.tabset}

* Covariates includes Gender, Euducation, Famly Income

### Parameters

```{r,fig.width=12, fig.height=6}
obj=fit.m1_total
kable(rbind(parameterestimates(obj,standardized = TRUE) %>% filter(lhs %in% c('flcs','slcs','mlcs','vlcs') & op == '~1') %>% select(-std.lv, -std.nox,-label),parameterestimates(obj,standardized = TRUE) %>% filter(lhs %in% c('flcs','slcs','mlcs','vlcs') & op=='~') %>% select(-std.lv, -std.nox,-label)
),
digits=3) %>%
  kable_styling(c("striped", "bordered"), full=F)
  
kable(t(data.frame(fit=fitMeasures(obj, c('cfi','tli','bic','rmsea','rmsea.ci.lower','rmsea.ci.upper','rmsea.pvalue')))),digits=3)%>%
  kable_styling(c("striped", "bordered"), full=F)
```

### Full summary
```{r}
summary(obj)
```

# Table3 {.tabset}

## Age + Baseline Intellect LA {.tabset}

### Parameters

```{r,fig.width=12, fig.height=6}
obj=fit.m1_cog
kable(rbind(parameterestimates(obj,standardized = TRUE) %>% filter(lhs %in% c('flcs','slcs','mlcs','vlcs') & op == '~1') %>% select(-std.lv, -std.nox,-label),parameterestimates(obj,standardized = TRUE) %>% filter(lhs %in% c('flcs','slcs','mlcs','vlcs') & op=='~') %>% select(-std.lv, -std.nox,-label)
),
digits=3) %>%
  kable_styling(c("striped", "bordered"), full=F)
  
kable(t(data.frame(fit=fitMeasures(obj, c('cfi','tli','bic','rmsea','rmsea.ci.lower','rmsea.ci.upper','rmsea.pvalue')))),digits=3)%>%
  kable_styling(c("striped", "bordered"), full=F)
```

### Full summary
```{r}
summary(obj)
```


## Age + Baseline social LA {.tabset}

### Parameters

```{r,fig.width=12, fig.height=6}
obj=fit.m1_soc
kable(rbind(parameterestimates(obj,standardized = TRUE) %>% filter(lhs %in% c('flcs','slcs','mlcs','vlcs') & op == '~1') %>% select(-std.lv, -std.nox,-label),parameterestimates(obj,standardized = TRUE) %>% filter(lhs %in% c('flcs','slcs','mlcs','vlcs') & op=='~') %>% select(-std.lv, -std.nox,-label)
),
digits=3) %>%
  kable_styling(c("striped", "bordered"), full=F)
  
kable(t(data.frame(fit=fitMeasures(obj, c('cfi','tli','bic','rmsea','rmsea.ci.lower','rmsea.ci.upper','rmsea.pvalue')))),digits=3)%>%
  kable_styling(c("striped", "bordered"), full=F)
```

### Full summary
```{r}
summary(obj)
```


## Age + Baseline Physical LA {.tabset}

### Parameters

```{r,fig.width=12, fig.height=6}
obj=fit.m1_phy
kable(rbind(parameterestimates(obj,standardized = TRUE) %>% filter(lhs %in% c('flcs','slcs','mlcs','vlcs') & op == '~1') %>% select(-std.lv, -std.nox,-label),parameterestimates(obj,standardized = TRUE) %>% filter(lhs %in% c('flcs','slcs','mlcs','vlcs') & op=='~') %>% select(-std.lv, -std.nox,-label)
),
digits=3) %>%
  kable_styling(c("striped", "bordered"), full=F)
  
kable(t(data.frame(fit=fitMeasures(obj, c('cfi','tli','bic','rmsea','rmsea.ci.lower','rmsea.ci.upper','rmsea.pvalue')))),digits=3)%>%
  kable_styling(c("striped", "bordered"), full=F)
```

### Full summary
```{r}
summary(obj)
```


# Table4 Interaction

## Total x Gender interaction {.tabset}

### Parameters

```{r,fig.width=12, fig.height=6}
obj=fit.m1_totalxgender
kable(rbind(parameterestimates(obj,standardized = TRUE) %>% filter(lhs %in% c('flcs','slcs','mlcs','vlcs') & op == '~1') %>% select(-std.lv, -std.nox,-label),parameterestimates(obj,standardized = TRUE) %>% filter(lhs %in% c('flcs','slcs','mlcs','vlcs') & op=='~') %>% select(-std.lv, -std.nox,-label)
),
digits=3) %>%
  kable_styling(c("striped", "bordered"), full=F)
  
kable(t(data.frame(fit=fitMeasures(obj, c('cfi','tli','bic','rmsea','rmsea.ci.lower','rmsea.ci.upper','rmsea.pvalue')))),digits=3)%>%
  kable_styling(c("striped", "bordered"), full=F)
```

### Full summary
```{r}
summary(obj)
```
